AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
mais fixes

Another problem faced by modern software companies and other
collectives are frequent ineffective meetings, which are seldom
focused to the interest to any attendant. The result is that it has
become the norm to participate in too many meetings with the ``laptop
open'', which can be un-productive. Software developers
like to code, to be productive, to have their hands on their project,
to do what they are best at. They dislike to forcibly stop for meetings
or to do other bureaucratic activities such as writing lengthy reports to justify their funding.
%\todo{ler mais. cacm, etc}

@@

A brief overview of current papers about GSD methodologies related with
AA is presented in Section~\ref{related-work}, while in
Section~\ref{aa-methodology} we describe the most relevant
characteristics of the AA methodology followed by the description of
our experience using AA in a team of 9 developers since July of
2011. Finally, in Section~\ref{conclusions}, we draw some final
conclusions and indicate future possibilities to the
practical use of AA on other teams of software developers or
individuals working on non-software activities.

@@

Various methodologies for GSD were built around the factors that
affect distributed team works, proposed by Carmel~\cite{carmel1999}
and comprising three distances: geographical, cultural and
temporal. Geographical distance prejudice \emph{coordination}, being
the act of integrating all the tasks distributed between
units~\cite{carmel2001}; \emph{control}, or the process to maintain
specific goals, policies or quality levels; and
\emph{communication}. All these factors are correlated, for example, a
team need to have clearly communication to work on tasks of a specific
problem. Cultural distance encompass differences on organizational and
natural culture. Spoken language, unit and ethnic values are common
forms of this distance. Some companies prefer to situate development
units in foreign locations with minimal cultural distance (e.g.\ an
American firm prefer Ireland, because of spoken language
similarity~\cite{carmel2001}). And finally the temporal distance that
prejudices synchronous communications like telephone or
videoconferences. Units of developers working on different time-zones
are concerned with managing of their agenda guided by this temporal
distance.

>>>>

Another problem faced by modern software companies and other
collectives are frequent ineffective meetings, which are seldom
focused to the interest to any attendant. The result is that it has
become the norm to participate in too many meetings with the ``laptop
open'', which can be un-productive. Software developers
like to code, to be productive, to have their hands on their project,
to do what they are best at. They dislike to forcibly stop for meetings
or to do other bureaucratic activities such as writing lengthy reports to
justify their funding.~\cite{Thompson:Wired:2012}
%\todo{ler mais. cacm, etc}

@@

A brief overview of current work on GSD methodologies related to
AA is presented in Section~\ref{related-work}, while in
Section~\ref{aa-methodology} we describe the most relevant
characteristics of the AA methodology followed by the description of
our experience using AA in a team of 9 paid developers 
% nao era mais de 9?
since July 2011. In Section~\ref{conclusions} we draw some final
conclusions and indicate future possibilities for the
practical use of AA in other types of software developers teams or
organizations working on non-software distributed activities.

@@

Various methodologies for GSD were built around the factors that
affect distributed team works, proposed by Carmel~\cite{carmel1999}
and comprising three distances: geographical, cultural and
temporal.

First, geographical distance handicaps ($i$) \emph{coordination}, the act of
integrating all the tasks distributed between units~\cite{carmel2001}; ($ii$)
\emph{control}, or the process to maintain specific goals, policies or quality
levels; and ($iii$) \emph{communication}. All those factors are correlated, \eg,
a team needs to have clear communication to work on tasks of a specific problem.

Second, cultural distance encompasses differences on organizational and
natural culture. Spoken language, unit and ethnic values are common
forms of such distance. Some companies prefer to allocate development
units in foreign locations with minimal cultural distance (\eg, an
American company may prefer Ireland due to spoken language
similarity~\cite{carmel2001}). Third, the temporal distance that
hampers synchronous communications like telephone or
videoconferences. Units of developers working on different time-zones
are concerned with managing of their agenda guided by this temporal
distance.
